Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-02-24 awipev-CO2.Rmd
seafet calibration period 1 updated

The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu°C.

@@

#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# set deployment period between 2 spectro measurements.
# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
                                ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
                                 ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
                                 ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
                                 ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
                                 ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
                                 ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
                                 ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
                                ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
                                ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
                                ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
                                ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
                                ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
                                ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
                                ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
                                ifelse(datetime >= sfinterv[26] , 26,NA )))))))))))))))))))))))))))

@@

# period 1, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 14:00:00" , mean_voltINT_4h, voltINT))

mean_voltEXT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltEXT = ifelse(datetime == "2017-08-24 14:00:00" , mean_voltEXT_4h, voltEXT))

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_insitu = ifelse(datetime == "2017-08-24 14:00:00" , mean_TseaF_4h, temp_insitu))

@@

  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#CCCCCC") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

# #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb,pHint_tot_sf)
# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
#     dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
# 
#   dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
#   dyLegend(show = "auto")   %>%
#   dyAxis( "y2",valueRange = c(-3, 36))%>%
#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#   dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

>>>>

The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu°C`.

@@

#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# set deployment period between 2 spectro measurements.
# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
                                ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
                                 ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
                                 ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
                                 ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
                                 ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
                                 ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
                                 ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
                                ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
                                ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
                                ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
                                #ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
                                #ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
                                #ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
                                #ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
                                ifelse(datetime >= sfinterv[22] , 22,NA )))))))))))))))))))))))

@@

# period 1, mean of 4 next hours for volt int + T seaF
mean_voltINT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltINT_4h, voltINT))

mean_voltEXT_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
d_all <- d_all%>%
  dplyr::mutate(voltEXT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltEXT_4h, voltEXT))

mean_TseaF_4h <- d_all%>%
  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
d_all <- d_all%>%
  dplyr::mutate(temp_insitu = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_insitu))

@@

  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#E0E0E0") %>%
  dyLegend(show = "auto")   %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)

# #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb,pHint_tot_sf)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
    dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%

  dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
    dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
  dyLegend(show = "auto")   %>%
  dyAxis( "y2",valueRange = c(-3, 36))%>%
  dyAxis( "y",valueRange = c(-2, 2))%>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30, dateWindow= NULL)
# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
